#------------------------------------------------------
# Author Aafaque Aafaque
# email: aafaqueabdullah@yahoo.com
#------------------------------------------------------

---
title: "Frequency"
author: "Aafaque"
date: "Thursday, January 29, 2015"
output: html_document
runtime: shiny
---
```{r}
  library(ggplot2)
  fbdata = read.table("Dynamic_Frequencies_Input.tsv",header=TRUE,sep='\t')
  xout <- table(fbdata$dob_day)
  xout
```

Frequency of Different attributes of facebook shown / Gender Wise

## Inputs and Outputs

User can Select Input to check Frequency against different attributes

Select BinWidth and Opacity of the Graph

Scale break of X-axis can also be selected like scale by 1 unit or 10 units visible.

Note: ggplot2 Package required

```{r, echo=FALSE}
inputPanel(
  selectInput("x_input", label = "Frequency Input",
              choices = names(fbdata), selected = "dob_day"),
  
  sliderInput("binw", label = "BinWidth",
              min = 0, max = 30, value = 1, step = 0.1),
  
  sliderInput("alpha", label = "Opacity of Bars in Histogram",
              min = 0, max = 1, value = 1, step = 0.1),
  
  sliderInput("xadjust", label = "X Scale Break Value",
              min = 0, max = 10, value = 1, step = 0.1)
)

renderPlot({
  summary(fbdata$dob_day)
  ggplot(fbdata, aes_string(x = (input$x_input), color="gender")) + geom_histogram(binwidth= input$binw, alpha= input$alpha) + scale_x_continuous(breaks = seq(from = 0, to = 10000, by = input$xadjust))

} , height = 1024 , width = 1024)
```