#---------------------------------------------------
# Developer: Aafaque Aafaque
# Email: aafaqueabdullah@yahoo.com
#---------------------------------------------------

---
title: "Multi Scatter Plots"
author: "Aafaque"
date: "Thursday, January 29, 2015"
output: html_document
runtime: shiny
---
```{r}
  library(ggplot2)
  diamonds = read.table("MultiScatterPlot_TestDataset.csv",header=TRUE,sep=',')
```

Pricing the C's of Diamond Stones

## Inputs and Outputs

In this we need to select x-y axis attributes to see reults, based on the third attrbibute (facet) , and also attribute can be selected to color out values scatter plot points , 

Number of Columns can be selected by user too

Scale break of X-axis can also be selected like scale by 1 unit or 10 units visible.
Note: ggplot2 Package required

```{r, echo=FALSE}
inputPanel(
  selectInput("x_input", label = "X-axis Input",
              choices = names(diamonds), selected = "carat"),
  
  selectInput("y_input", label = "Y-axis Input",
              choices = names(diamonds), selected = "price"),
  
  selectInput("facet", label = "Facetting Attribute",
              choices = names(diamonds), selected = "cut"),
  
  selectInput("color", label = "Color Attribute",
              choices = names(diamonds), selected = "cut"),
  
  sliderInput("xadjust", label = "X Scale Break Value",
              min = 0, max = 10, value = 1, step = 0.1),
  
  sliderInput("col", label = "Columns to Show",
              min = 1, max = 10, value = 1, step = 1)
)

renderPlot({
  ggplot(data = diamonds, aes_string(x = (input$x_input), y = (input$y_input)  ,color = (input$color) )) + geom_point() + facet_wrap((input$facet),ncol = input$col) + scale_x_continuous(breaks = seq(from = 0, to = 10000, by = input$xadjust))

} , height = 1024 , width = 1024)
```